Supporting Information

### 2021-10-25 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p7
graphics.off()

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

>>>>

dev.new()
png("q1_2_new.png", width = 1400, height = 2200)
p75
graphics.off()

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)
